strucplots---Visualizing higher-dimensional Contingency Tables in \pkg{vcd}

### 2005-08-30 trunk/vcd/inst/doc/strucplot.Rnw
mosaic,assoc,and sieve now also accept structable objects. as.table.structable and plot.structable added.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/vcd@452 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

<<changeplot>>=
assoc(Titanic)
getNames() ## output not shown
grid.edit("rect:Class=1st,Age=Adult,Sex=Female,Survived=Yes", 
            gp = gpar(fill = "red"))
@

>>>>

<<changeplot>>=
assoc(Titanic, pop = FALSE)
getNames() ## output not shown
grid.edit("rect:Class=1st,Sex=Female,Age=Adult,Survived=Yes", 
            gp = gpar(fill = "red"))
@
